{Simulating the Brownian Dynamics of a Two-dimensional Model for the Dynein Motor Protein}\vspace{1.5em}\\ \includegraphics[width=0.5\columnwidth]{OSU_logo.png}\vspace{0.5em}\\ \large{Oregon State University}

### 2019-04-30 papers/waczak-thesis/thesis/chapters/theory.tex
thesis update

	\section{Binding and Unbinding}
	To keep the simulation simple, we have chosen a very physically reasonable and uncomplicated binding model with a minimum amount of assumptions. The two key processes, binding and unbinding, are controlled by two parameters called the binding rates. For binding, we simply assume that a binding event occurs when a binding domain is close enough to the microtubule. In other words
	\begin{equation}
		\rho_{b} = k_b
	\end{equation}
	where $\rho_b$ is a probability per second and $k_b$ is a constant. \\

>>>>

	\section{Binding and Unbinding}
	To keep the simulation simple, we have chosen a very physically reasonable and uncomplicated binding model with a minimum amount of assumptions. The two key processes, binding and unbinding, are controlled by two parameters called the binding rates. For binding, we simply assume that a binding event occurs at a certain rate whenever a binding domain is close enough to the microtubule. That is,

	\begin{equation}
	\begin{cases}
		\rho_{b} = k_b; & y_b < \varepsilon \\ 
		\rho_{b} = 0; & y_b > \varepsilon
	\end{cases}
	\end{equation}

	where $\rho_b$ is a probability per second and $k_b$ is a constant. \\
